Transforming Trash as an Artistic Act

### 2016-01-17 chapter2_final.tex
Print copy preperations, proof reading
Former-commit-id: c4e7e2d53515fdd32b70a48f44d38c9e790b69b9

Firstly, I focused on the disposable items that are designed to be ended up in waste bin after a single use. Their usage and place are examined in the society and how other artists used and transformed them is analyzed. Further, disposable items are one of the key material used in the thesis project. Therefore, they need to be discussed in detail. Secondly, I looked through the Žižek’s comments on ecological perspectives that dominate the approaches on rubbish. Lastly, through \quotes{Rubbish Theory} transformation of trash and its various states as an object category is examined.

@@

According to findings of archaeologist Daniel Ingersoll the age of the throwaway world began not in the twentieth century but during the nineteenth \citep[as cited in][41]{rathje1992rubbish} On the other hand, scholars have criticized the notion of \quotes{throwaway society} as being insufficient and over generalization of consumer behavior \citep{gregson2007identity}. According to the result of their qualitative research on consumers over two-year people are not as wasteful as claimed when considering household possessions such as television, furniture and toys. However, their research did not include disposable packaging and bottles. Therefore, the act of throwing away can be narrowed down to the specific goods.

@@

% Disposable Items
Disposable items are made to be thrown away after used once or only a few times. They are not permanent or durable and not designed to reuse again. Packages of beverages, paper cups and tissues are some of them. They are used very short-time. Their lifetime can be measured in minutes in terms of usage. However, their usage duration is very short, they continue to exist in nature.

@@

The remarkable thing about many of these objects ---especially those produced in the last of the twentieth century--- is that they were specifically designed to end up on the garbage heap \citep{cerny1996recycled}. They were designed to decrease in value over time to be used one, or twice and then to be thrown away. This applies not only applies packing ---designed containers that protect and promote products--- but to an ever expanding list of products. \quotes{When an object is discarded, it is perceived as being no longer of value to the person or society that once possessed it. Once a newspaper is read, or a bottle of coca cola consumed, its basic function is fulfilled, and it is intended to be thrown out as trash} \citep{cerny1996recycled}.

@@

Technological advancements can be one of the factors that cause over-consumption habits. Disposable items with the help of industrialization can be produced easily. Disposable items reduce the labor and human resources as compared to the traditional ways. For instance, consider napkin(tissue, towel) versus wipes, glass versus paper cup. Another point is that they are more affordable regarding supply chain and cost. In other words, people can put new one easily. Therefore, there is no need to save the old one. The last but not least increasing attention of hygiene is contributed to the extension of disposables in the market highly. \quotes{The commodities of food and drink must be safe, sterile and private} \citep[70]{kennedy2007ontology}.

@@

% ARTWORK
% Portraits of Global Mass culture
\begin{figure}[h!]
\begin{subfigure}{.48\textwidth}
  \centering
  \includegraphics[width=\linewidth]{graphics/ChrisJordan_Numbers_OriginalView.jpg}
  \caption{Original view}
  \label{fig:ChrisJordan_Numbers_OriginalView}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
  \centering
  \includegraphics[width=\linewidth]{graphics/ChrisJordan_Numbers_CloseView.jpg}
  \caption{Close view}
  \label{fig:ChrisJordan_Numbers_CloseView}
\end{subfigure}
\caption{Chris Jordan, \textit{Caps Seurat}, 2011, Offset print, 60x90" in one panel, and 88x132" in 3 panels}
\label{fig:ChrisJordan_Numbers_CapsSeurat}
\end{figure}

@@

\textit{Caps Seurat} shown in figure \ref{fig:ChrisJordan_Numbers_CapsSeurat} displays four hundred thousand plastic bottle caps all together. \quotes{It equal[s] to the average number of plastic bottles consumed in the United States in every minute} says Jordan. It is one of the piece of Portraits of Global Mass Culture by photographer Chris Jordan. In this series, he revisits the statistics of modern societies. \cite{boustead2015impossible} explains that \quotes{Chris Jordan attempts to convey the vastness of modern consumption by breaking down annual statistics into more graspable quantities depicted by clever visualizations made of individual objects or groups of objects that he photographs.} Jordan says that \quotes{[t]here’s a disconnect that happens when we assume we know what we’re talking about when we talk about hundreds of millions of plastic bottles} \citep[as cite in][]{boustead2015impossible}. He argues that \quotes{translating these numbers from the deadening language of statistics into a visual language that allows some kind of comprehension} \citep[as cite in][]{boustead2015impossible}. He creates these works through the combining photographic illustration of everyday trash and mass consumption leftover. He draws attention to the blind unawareness entangled in consumerism. His work, while often disturbing, is a strong message about ignorant practices in people's everyday lives, leaving it to the viewer to draw conclusions about the unavoidable consequences which will originate from people's daily consumption routines. He recreates the most remarkable artworks with combining bits of trashes as a mosaic. Here he draws attention to the our consumerism and express them in visuals and all the material that we have in these days is trash to create this pictures.

@@

% ARTWORK
% COFFEE CUP
\begin{figure}[h!]
\begin{subfigure}{.48\textwidth}
  \centering
  \includegraphics[width=\linewidth]{graphics/Gwyneth-Leech-cup5.jpg}
  \caption{Installation view}
  \label{fig:GwynethLeech_Installation}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
  \centering
  \includegraphics[width=\linewidth]{graphics/Gwyneth-Leech-cup3.jpg}
  \caption{Painting in the public}
  \label{fig:GwynethLeech_Public}
\end{subfigure}
\caption{Gwyneth Leech, \textit{365 A Year in Cups}, 2013, Mixed media on upcycled paper coffee cups, Dimensions variable}
\label{fig:GwynethLeech_CoffeeCups}
\end{figure}

@@

Song’s mother, Zhao Xiangyuan (1938–2009), was typical person of the generation of Chinese who lived through the poverty of the Cultural Revolution in the third quarter of twentieth century century by the saying \textit{wu jin qi yong} (waste not). As a result, all commodities owned or collected items are stockpiled and preserved as protection against for future poverty, even in the times of improving economic conditions.

@@

Jane Alison, senior curator at the Barbican Art Gallery in London, states that \quotes{\textit{Waste Not} helps us to understand the reality of Chinese history and culture in the twentieth century century in a way that newspapers can’t} \citep[as cited in][]{needham2015chinese}

As it can be understood trash reflects people's habits. It is like a mirror. It can not be separated from their producers and it is well studied area by scholars. Garbology is a study of waste as a social science. It applies methodologies of archeology to the human debris. Weberman infamously used techniques of what he deemed garbology to uncover what he saw as the essential nature of people. He once said, perhaps indirectly referencing Jean Brillat-Savarin’s quote about food, \quotes{You are what you throwaway} \citep[as cited in][301]{lukas2012garbage}. The field of garbology involves the study of refuse and waste. It enables researchers to document information on the dump and changing patterns of modern rubbish, hence assisting in the study of contemporary human society or culture \citep{roy2012garbology}. According to the Oxford English Dictionary, the term was first used by waste collectors in the 1960s. Weberman popularized the term in describing his study of Bob Dylan’s garbage in 1970. It was pioneered as an academic discipline by William Rathje at the University of Arizona in 1973. The work of archaeologists such as William Rathje and Cullen Murphy has offered significant insights into the relationship between archaeological artifacts and garbage, exploring the function of trash as a resource for understanding the cultural and social practice. With the help of mentioned understanding of trash, what can be understand from the works of art?

@@

Every detail of Emin's private life is presented through her bed in an uncensored fashion. The idea of \textit{My Bed} (Figure \ref{fig:TraceyEmin_MyBed}) was result of a depressive period in the artist’s life when she had stayed in bed for a few days without eating or drinking anything except alcohol. The feeling of depression resulting in mess and detritus is not completely unusual to many people, and \textit{My Bed} therefore has a bold affect on the viewer. The artwork generated great media enthusiasm, particularly over the fact that the bed sheets were stained with bodily secretions and the floor had items from the artist’s room, such as condoms, underwear with menstrual blood stains, other junks, and functional, everyday objects, including a pair of slippers.

@@

% TODO buarada aşağısını toparlamak gerekli.
In the light of Žižek’s arguments ecology is not an appropriate (or enough) point to approach trash. He points out the need for the new approach to trash. This new approach should not idealize it. At this point where the practices of art gains importance to establish new understanding of trash.

Not every act of transforming trash is not related to ecological concerns. Artists are not trying to save the planet earth. Beyond ecological concerns, they are attempting to find new ways to look and live with trash.

Some artists turned to trash into site-specific sculptures that are more than trash heap after their intervention. Not discarding but bracing our attitudes turned them to a something that worth it to watch and think about it. (Converting what we create harmonious with the existing system. Because it is not possible to think that nature will live harmoniously with what we created. The more reasonable idea will be we will live harmoniously with what we create.) Turning trash to things that can be lived together.

In the light of this arguments the idealization of nature is problematic. Loving nature is loving it with all dimensions. Live with trash. Do not see it as trash. Then the question is How to love trash? How to live with trash? Think beyond the common perception. Do not consider it as abject, disgust. Can live with our trash enrich our perceptions and abilities? How not to see them as trash and useless? Can it be possible with art?

@@

It can be claimed that the end of an object’s life equates to the moment when it is refused. As stated by \citet[63]{emgin2012trashion} this action \quotes{might take place in different forms and for [various] reasons.} In common sense it is considered as waste. At this moment, the object is left valueless in all the possible meanings of the term value. It can no more serve a function, it can on no account be exchanged for anything else, and it can by no means engage in the processes of signification to connote and endow its user with specific social values \citep[63]{emgin2012trashion}. However, Thompson’s Rubbish Theory shows us the opposite of it. Trash can is not an end it is starting point of another life.

In \singlequotes{The Social Life of Things} \citet[3]{appadurai1988social} highlights that \quotes{commodities, like persons, have social lives.} Similarly, \cite{kopytoff1986cultural} notes that the biography of an object was considerably similar to that of a person: occupying different positions, leading diverse careers in the course of different periods between a beginning and an end, being defined by different systems of value that are both economically and culturally inscribed. Appadurai focuses on the \quotes{commodity potential} of things and asserts that \quotes{things can move in and out of the commodity state, that such movements can be slow or fast, reversible or terminal, normative or deviant} (1986: 13). However, one can ask that what are these commodity states and does anything exist between them? Thompson’s Rubbish Theory fills this gap.

Thompson observes the creation and destruction of value in produced gadgets, cultural artifacts, and ideas. He notes that how an object’s economic and cultural value diminishes over time rendering the objects worthless or redundant and how others value increases overtime. In his notable Rubbish Theory, he declares three object states; transient (normal state, decreasing value, circulating), durable (permanent, increasing value, removed from circulation) and rubbish (zero value, will be destroyed or reinvested for economic and social value). The transient category falls into the common state of objects that are lessening in value and have limited life period. A used car can be an example of transient state. On the contrary, the durable objects’ value increase over time and have preferably unlimited life spans. Antiques and objects in museums can be an example of durable. This theory gives rubbish a key role between transient and durable.

Rubbish is, by definition, an object that is not or is no longer, owned by anyone, which falls outside all categories of economics, culture, and social control. As one of many things on the garbage heap, a discarded object even tends to take on a negative value as something unsanitary, dangerous. The socially constructed value of the object has shifted over time from its limited life span of usefulness and meaning to a infinite and valuable socially accepted rubbish.

The potential of the discarded material also relies on its status as an object approaching a zero point of value. In other words, it has reached a point in transition between the world of the functioning, the useful and visible, and the realm of the invisible, the non-functioning and empty. As Michael Thompson’s Rubbish Theory suggests that rubbish is both ready for the disappearance and yet ripe for reinvestment, reinterpretation or revaluing. Trash as a state of being flexible is ready to transformation.

@@

As argued by Thompson, rubbish represents a remarkable in-between ---middle--- category in a area of flexibility which is not exposed to the same control systems of the valuable and socially considerable categories of transient and durable. Hence, it \quotes{is able to provide the path for the seemingly impossible transfer of an object from transience to durability} (1979: 9) he also puts forward that \quotes{a transient object gradually declining in value and in expected life span may slide across into rubbish} (1979: 9) where it has the chance of being re-discovered, brought to light or admired once again. Figure \ref{fig:rubbish_theory} demonstrates the possible paths an object may take (from transient to rubbish and from rubbish to durable). The transitions between these states are defined as follows: from transient to rubbish (transient -> rubbish) and from rubbish to durable (rubbish -> durable).

% TODO
\begin{figure}[h!]
  \centering
  \includegraphics[height=4cm]{graphics/rubbish_theory.jpg}
  \caption{Thompson’s Rubbish Theory}
  \label{fig:rubbish_theory}
\end{figure}

To illustrate rubbish theory the series of compression by French sculpture César can be analyzed in the context of it. His early work is composed of soldered and welded metal as well as junk materials. In 1960, Caesar discovered the hydraulic press that is capable of compacting scrap metal (especially car bodies) during on a visit to a scrap merchant in search of metal. He admired from the hydraulic crushing machine in operation and started to experiment with it in his sculptures. The machine is used to compress the metal items in order to gain from space. His first three automobile compression exhibited at Salon de Mai in 1960 and bring him a supportive fame. Later Viscountess Marie-Laure de Noailles who is important figure of these ages, gave him her Zim model car to compress. It is 
% http://www.sothebys.com/en/auctions/ecatalogue/2015/art-contemporain-pf1515/lot.6.html
\quotes{a revolutionary artistic gesture then, but also a strong political gesture, right in the middle of the Cold War; César having chosen to lash out against a Zim, a jewel of the Soviet automobile industry commissioned by Khrushchev at the beginning of the 1950s to compete with the Cadillac.} Additionally car was one of the most desired possessions of people in twentieth century century. Through the eyes of rubbish theory it is a transient object and after the intervention of artist, it is transformed into an artwork that preserved in the collection of Museum. In other words, it switched to durable category by interestingly trashing it.

% Bu iş dolaşımdaki olan bir şeyi alıp, onu çöpleştiriyor. Ama bunu yapması ile birlikte yapıldığı bağlam, hikayesi, çevresindeki insanlar, sanatçı hepsi birlikte onu müzede sergilenen, açık arttırmaya çıkar hale getiriyor.

\begin{figure}[h!]
  \centering
  \includegraphics[height=10cm]{graphics/Cesar_Zim.jpg}
  \caption{César, \textit{Compression Zim}, 1960-1961, 157 x 82 x 64 cm}
  \label{fig:Cesar_Zim}
\end{figure}

Although Thompson is quite successful describing states of objects, claimed transitions between states in the theory have some problems. Thompson label some transitions as possible and the others as impossible. He only allows movement of goods from transient to rubbish, and from rubbish to durable. Movement in the other directions, from durable to either transient or rubbish, does not exist in this system. However, Duchamp’s notable ready-made \textit{Fountain} is one of the examples outside of the defined transitions.

\textit{Fountain} (1917) is a artwork produced by Marcel Duchamp, who is notable member of provocative Dada movement. The piece was an industrial porcelain urinal, which was signed \quotes{R.Mutt}. It is submitted for the exhibition of the Society of Independent Artists in 1917. Committee rejected \textit{Fountain}, even though the rules declared that all works would be accepted from artists who paid the fee. It is considered one of the major artworks of the twentieth century century because of challenging the existing understanding of art. Duchamp used already existing fabricated ordinary urinal to express his ideas by challenging existing way of art making which requires efforts of the artist. It forces to the limits of the language of art and perception the art. To understand his works requires shift inside of the peoples mind. For him, the idea is important rather than the object. He also criticized the position of artist by signing urinal as \quotes{R.Mutt} who is actually not exist. In the editorial The Blind Man summarized this work as follows: \quotes{Whether Mr. Mutt with his own hands made the fountain or not has no importance. He CHOSE it. He took an ordinary article of life, placed it so that its useful significance disappeared under the new title and point of view --- created a new thought for that object} \citep{duchamp1917mutt}. To debate all the aspects of this work is not possible with the scope of this thesis. However when it is analyzed through the frame of rubbish theory, urinal a transient object turned to durable objects that are exhibited by the intervention of artist. Urine titled as \textit{Fountain} is still functional and have a place in the market. In another word, it is not rubbish.

>>>>

Firstly, I focused on the disposable items that are designed to be ended up in waste bin after a single use. Their usage and place are examined in the society and how other artists used and transformed them is analyzed. Further, disposable items are one of the key material used in the thesis project. Therefore, they need to be discussed in detail. Secondly, I looked through the Žižek’s comments on ecological perspectives that dominate the approaches on rubbish. Lastly, through \textit{Rubbish Theory} transformation of trash and its various states as an object category is examined.

@@

According to findings of archaeologist Daniel Ingersoll the age of the throwaway world began not in the twentieth century but during the nineteenth century \citep[as cited in][41]{rathje1992rubbish}. On the other hand, scholars have criticized the notion of \quotes{throwaway society} as being insufficient and over generalization of consumer behavior \citep{gregson2007identity}. According to the result of their qualitative research on consumers over two-year, people are not as wasteful as claimed when considering household possessions such as television, furniture and toys. However, their research did not include disposable packaging and bottles. Therefore, the act of throwing away can be narrowed down to the specific goods.

@@

% Disposable Items
Disposable items are made to be thrown away after used once or only a few times. They are not permanent or durable and not designed to be reused again. Packages of beverages, paper cups and tissues are some of them. They are used very short-time. Their lifetime can be measured in minutes in terms of usage. Although, their usage duration is very short, they continue to exist in nature.

@@

The remarkable thing about many of these objects ---especially those produced in the last of the twentieth century--- is that they were specifically designed to end up on the garbage heap \citep{cerny1996recycled}. They were designed to decrease in value over time to be used one, or twice and then to be thrown away. This applies not only packing ---designed containers that protect and promote products--- but to an ever expanding list of products. \quotes{When an object is discarded, it is perceived as being no longer of value to the person or society that once possessed it. Once a newspaper is read, or a bottle of coca cola consumed, its basic function is fulfilled, and it is intended to be thrown out as trash} \citep{cerny1996recycled}.

@@

Technological advancements can be one of the factors that cause over-consumption habits. Disposable items with the help of industrialization can be produced easily with low cost and they reduce the labor and human resources as compared to the traditional ways. For instance, consider handkerchief versus napkin, glass versus paper cup. Another point is that they are more affordable regarding supply chain and cost. In other words, people can put new one easily after disposing it. Therefore, there is no need to save the old one. The last but not least increasing attention of hygiene is contributed to the extension of disposables in the market highly. \quotes{The commodities of food and drink must be safe, sterile and private} \citep[70]{kennedy2007ontology}.

@@

% ARTWORK
% Portraits of Global Mass culture
\begin{figure}[h!]
\begin{subfigure}{.48\textwidth}
  \centering
  \includegraphics[width=\linewidth]{graphics/ChrisJordan_Numbers_OriginalView.jpg}
  \caption{Original view}
  \label{fig:ChrisJordan_Numbers_OriginalView}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
  \centering
  \includegraphics[width=\linewidth]{graphics/ChrisJordan_Numbers_CloseView.jpg}
  \caption{Close view}
  \label{fig:ChrisJordan_Numbers_CloseView}
\end{subfigure}
\caption{Chris Jordan, \textit{Caps Seurat}, 2011, Digital pigment print, 60x90" in one panel, and 88x132" in 3 panels}
\label{fig:ChrisJordan_Numbers_CapsSeurat}
\end{figure}

@@

\textit{Caps Seurat} shown in figure \ref{fig:ChrisJordan_Numbers_CapsSeurat} displays four hundred thousand plastic bottle caps all together. \quotes{It equal[s] to the average number of plastic bottles consumed in the United States in every minute} says Jordan. It is one of the piece of Portraits of Global Mass Culture by photographer Chris Jordan. In this series, he revisits the statistics of modern societies. \cite{boustead2015impossible} explains that \quotes{Chris Jordan attempts to convey the vastness of modern consumption by breaking down annual statistics into more graspable quantities depicted by clever visualizations made of individual objects or groups of objects that he photographs.} Jordan says that \quotes{[t]here’s a disconnect that happens when we assume we know what we’re talking about when we talk about hundreds of millions of plastic bottles} \citep[as cite in][]{boustead2015impossible}. He argues that \quotes{translating these numbers from the deadening language of statistics into a visual language that allows some kind of comprehension} \citep[as cite in][]{boustead2015impossible}. He creates these works through the combining photographic illustration of everyday trash and mass consumption leftover. He draws attention to the blind unawareness entangled in consumerism. His work, while often disturbing, is a strong message about ignorant practices in people’s everyday lives, leaving it to the viewer to draw conclusions about the unavoidable consequences which will originate from people’s daily consumption routines. He recreates the most remarkable artworks with combining bits of trashes as a mosaic. Here he draws attention to the our consumerism and express them in visuals and all the material that we have in these days is trash to create this pictures.

@@

% ARTWORK
% COFFEE CUP
\begin{figure}[h!]
\begin{subfigure}{.48\textwidth}
  \centering
  \includegraphics[width=\linewidth]{graphics/Gwyneth-Leech-cup5.jpg}
  \caption{Installation view}
  \label{fig:GwynethLeech_Installation}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
  \centering
  \includegraphics[width=\linewidth]{graphics/Gwyneth-Leech-cup3.jpg}
  \caption{Painting in the public}
  \label{fig:GwynethLeech_Public}
\end{subfigure}
\caption{Gwyneth Leech, \textit{365 A Year in Cups}, 2013, Mixed media on upcycled paper cups, Dimensions variable}
\label{fig:GwynethLeech_CoffeeCups}
\end{figure}

@@

Song’s mother, Zhao Xiangyuan (1938–2009), was typical person of the generation of Chinese who lived through the poverty of the Cultural Revolution in the third quarter of twentieth century by the saying \textit{wu jin qi yong} (waste not). As a result, all commodities owned or collected items are stockpiled and preserved as protection against for future poverty, even in the times of improving economic conditions.

@@

Jane Alison, senior curator at the Barbican Art Gallery in London, states that \quotes{\textit{Waste Not} helps us to understand the reality of Chinese history and culture in the twentieth century in a way that newspapers can’t} \citep[as cited in][]{needham2015chinese}

As it can be understood trash reflects people’s habits. It is like a mirror. It can not be separated from their producers and it is well studied area by scholars. Garbology is a study of waste as a social science. It applies methodologies of archeology to the human debris. Weberman infamously used techniques of what he deemed garbology to uncover what he saw as the essential nature of people. He once said, perhaps indirectly referencing Jean Brillat-Savarin’s quote about food, \quotes{You are what you throwaway} \citep[as cited in][301]{lukas2012garbage}. The field of garbology involves the study of refuse and waste. It enables researchers to document information on the dump and changing patterns of modern rubbish, hence assisting in the study of contemporary human society or culture \citep{roy2012garbology}. According to the Oxford English Dictionary, the term was first used by waste collectors in the 1960s. Weberman popularized the term in describing his study of Bob Dylan’s garbage in 1970. It was pioneered as an academic discipline by William Rathje at the University of Arizona in 1973. The work of archaeologists such as William Rathje and Cullen Murphy has offered significant insights into the relationship between archaeological artifacts and garbage, exploring the function of trash as a resource for understanding the cultural and social practice. With the help of mentioned understanding of trash, what can be understand from the works of art?

@@

Every detail of Emin’s private life is presented through her bed in an uncensored fashion. The idea of \textit{My Bed} (Figure \ref{fig:TraceyEmin_MyBed}) was result of a depressive period in the artist’s life when she had stayed in bed for a few days without eating or drinking anything except alcohol. The feeling of depression resulting in mess and detritus is not completely unusual to many people, and \textit{My Bed} therefore has a bold affect on the viewer. The artwork generated great media enthusiasm, particularly over the fact that the bed sheets were stained with bodily secretions and the floor had items from the artist’s room, such as condoms, underwear with menstrual blood stains, other junks, and functional, everyday objects, including a pair of slippers.

@@

In the light of Žižek’s arguments ecology is not an appropriate (or enough) point to approach trash. He points out the need for new approaches to trash. This new approach should not idealize nature and trash. At this point, the practices of art gain importance to establish new understanding of trash. Not every act of transforming trash is not related to ecological concerns. Artists are not trying to save the planet earth. Beyond ecological concerns, they are attempting to find new ways to look and live with trash. Some artists turned to trash into site-specific sculptures that are more than trash heap after their intervention. Not discarding but embracing people's trash, they turned them to a something that worth it to watch and think about it. They convert what people throw away into objects that are harmonious with the existing system because it is not possible to think that nature will live harmoniously with what people created. The more reasonable idea will be people will live harmoniously with what they create. Their action can be seen as turning trash to things that can be lived together.

In the light of this arguments the idealization of nature is problematic. Loving nature is loving it with all dimensions. His suggestion is to find a way to live with trash instead of seeing it as trash. Then the question becomes how to love and live with trash? Think beyond the common perception. Do not consider it as abject, disgust. Can live with our trash enrich our perceptions and abilities? How not to see them as trash and useless? Can it be possible with art?

@@

It can be claimed that the end of an object’s life corresponds to the moment when it is refused. As stated by \citet[63]{emgin2012trashion} this action \quotes{might take place in different forms and for [various] reasons.} In common sense, trash can or dump is the graveyard of objects. In landfills, \quotes{the object is left valueless} in all kinds various value system. \quotes{It can no more serve a function, it can on no account be exchanged for anything else, and it can by no means engage in the processes of signification to connote and endow its user with specific social values} \citep[63]{emgin2012trashion}. However, Thompson’s \textit{Rubbish Theory} shows us the opposite of it. Trash can is not an end it is starting point of another life.

In \textit{The Social Life of Things} \citet[3]{appadurai1986social} highlights that \quotes{commodities, like persons, have social lives.} Similarly, \citet[66]{kopytoff1986cultural} notes that the biography of a thing was significantly similar to an account of someone’s life. It moves into different positions, and experiences diverse paths in the course of different states and different systems of value that are both economically and culturally defined. Appadurai focuses on the \quotes{commodity potential} of things and asserts that \quotes{things can move in and out of the commodity state, that such movements can be slow or fast, reversible or terminal, normative or deviant} (1986: 13). However, one can ask that what are these commodity states and does anything exist between them? Thompson’s \textit{Rubbish Theory} fills this gap.

Thompson observes the creation and destruction of value in products, cultural artifacts, and ideas. He notes that how an item’s economic and cultural value lessen through time rendering the objects unprofitable or unnecessary and how others’ value increases. In his notable \textit{Rubbish Theory}, he declares three object states; transient (normal state, decreasing value, circulating), durable (permanent, increasing value, removed from circulation) and rubbish (zero value, will be destroyed or reinvested for economic and social value). The transient category falls into the common state of objects that are lessening in value and have limited life period. A used car can be an example of transient state. On the contrary, the durable objects’ value increase through time and have probably unlimited life spans. Antiques and objects in museums can be an example of durable. This theory gives rubbish a key role between transient and durable.

Rubbish is, by definition, an object state that is not or is no longer, owned by anyone, which falls outside all kinds of economics, culture, and social system. As one of many things on the garbage heap, a discarded object even tends to take on a negative value as something unsanitary, dangerous. However the socially constructed value of the object can shift through time from its limited life span of usefulness and meaning to a infinite and valuable socially accepted rubbish.

The potential of the discarded material also relies on its status as an object approaching a zero point of value. In other words, it has reached a point in transition between the world of the functioning, the useful and visible, and the realm of the invisible, the non-functioning and empty. Its value and function open to be reset. As Thompson suggests that rubbish is both ripe for disappearance and yet suitable for reinterpretation, reinvestment or revaluing. Further rubbish as a state of being flexible is ready to transformation.

@@

As argued by Thompson, rubbish represents a remarkable in-between ---middle--- category in a area of flexibility which is not exposed to the same control systems of the valuable and socially considerable categories of transient and durable. Hence, it \quotes{is able to provide the path for the seemingly impossible transfer of an object from transience to durability} (1979: 9) he also puts forward that \quotes{a transient object gradually declining in value and in expected life span may slide across into rubbish} (1979: 9) where it has the chance of being re-discovered, brought to light or admired once again. In other words, he specifies the path between the object categories. The path of transitions between transient, rubbish and durable objects are defined as follows: from transient to rubbish (transient -> rubbish) and from rubbish to durable (rubbish -> durable).

To illustrate \textit{Rubbish Theory} the series of compression by French sculpture César can be analyzed in the context of it. His early work is composed of soldered and welded metal as well as junk materials. In 1960, Caesar discovered the hydraulic press that is capable of compacting scrap metal (especially car bodies) during on a visit to a scrap merchant in search of metal. He admired from the hydraulic crushing machine in operation and started to experiment with it in his sculptures. The machine is used to compress the metal items in order to gain from space. His first three automobile compression exhibited at Salon de Mai in 1960 and bring him a supportive fame. Later Viscountess Marie-Laure de Noailles who is important figure of these ages, gave him her Zim model car to compress. It is 
% http://www.sothebys.com/en/auctions/ecatalogue/2015/art-contemporain-pf1515/lot.6.html
\quotes{a revolutionary artistic gesture then, but also a strong political gesture, right in the middle of the Cold War; César having chosen to lash out against a Zim, a jewel of the Soviet automobile industry commissioned by Khrushchev at the beginning of the 1950s to compete with the Cadillac.} Additionally car was one of the most desired possessions of people in twentieth century. Through the eyes of rubbish theory it is a transient object and after the intervention of artist, it is transformed into an artwork that preserved in the collection of Museum. In other words, it switched to durable category by interestingly trashing it.

\begin{figure}[h!]
  \centering
  \includegraphics[height=10cm]{graphics/Cesar_Zim.jpg}
  \caption{César Baldaccini, \textit{Compression Zim}, 1960-1961, 157 x 82 x 64 cm}
  \label{fig:Cesar_Zim}
\end{figure}

Although Thompson is quite successful describing states of objects, claimed transitions between object categories in the theory have some problems. Thompson label some transitions as possible and the others as impossible. He only allows movement of goods from transient to rubbish, and from rubbish to durable. Movement in the other directions, from durable to either transient or rubbish, does not allowed in this system. However, Duchamp’s notable ready-made \textit{Fountain} is one of the examples that fall outside of the given transitions.

\textit{Fountain} (1917) is an artwork produced by Marcel Duchamp, who is notable member of provocative Dada movement. The piece was an industrial porcelain urinal, which was signed \quotes{R.Mutt}. It is submitted for the exhibition of the Society of Independent Artists in 1917. Committee rejected \textit{Fountain}, even though the rules declared that all artworks would be accepted from artists who paid the fee. It is considered one of the major artworks of the twentieth century because of challenging the existing understanding of art. Duchamp used already existing fabricated ordinary urinal to express his ideas by challenging existing way of art making which requires efforts of the artist. It forces to the limits of the language of art and perception the art. To understand his works requires shift inside of the peoples mind. For him, the idea is important rather than the object. He also criticized the position of artist by signing urinal as \quotes{R.Mutt} who is actually not exist. In the editorial The Blind Man summarized this work as follows: \quotes{Whether Mr. Mutt with his own hands made the fountain or not has no importance. He CHOSE it. He took an ordinary article of life, placed it so that its useful significance disappeared under the new title and point of view --- created a new thought for that object} \citep{duchamp1917mutt}. To debate all the aspects of this work is not possible with the scope of this thesis. However when it is analyzed through the frame of rubbish theory, urinal a transient object turned to durable objects that are exhibited by the intervention of artist. Urine titled as \textit{Fountain} is still functional and have a place in the market. In another word, it is not rubbish.
